Breadth First Searches Over Evolving Graphs

### 2016-01-24 paper.tex
fix typo and community searching in application

Then given an author $a$ at time $t_1$, the evolving graph BFS described above
can compute $T(a, t_1)$, the set of all the authors that have been influenced by
$a$'s work at time $t_1$.
Define also a \emph{community} to be a group of
researchers that have been influenced by the same authors.
For example, given a paper published by $a$ at time $t$,
we can determine $a$'s community by searching backward in time to find
$T^-1(a, t_1)$, the authors that influenced $a$ at time $t$, and also searching
forward to find $T(a, t_1)$.
The backward search in time follows straightforwardly from the forward time traveral
presented above simply by reversing the time labels, e.g.\ by the transformation
$t\rightarrow -t$.

>>>>

Then given an author $a$ at time $t_1$, the evolving graph BFS described above
can compute $T(a, t_1)$, the set of all the authors that have been influenced by
$a$'s work at time $t_1$.
Define also a \emph{community} to be a group of
researchers that have been influenced by the same authors.
For example, given a paper published by $a$ at time $t$,
we can determine $a$'s community by searching backward in time to find
$T^{-1}(a, t)$, the authors that influenced $a$ at time $t$, and then searching
forward to find $T(l_1, t_1) \cup T(l_1, t_2) \cup \cdots \cup T(l_k, t_k)$, where 
$(l_1,t_1), (l_2, t_2), \ldots, (l_k, t_k)$ are the leaves of $T^{-1}(a,t)$.
The backward search in time follows straightforwardly from the forward time traveral
presented above simply by reversing the time labels, e.g.\ by the transformation
$t\rightarrow -t$.
